Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-08-31 WSSSPE3/report/WSSSPE3_review.tex
adding footnote URLs for Hwang talks

\item \textbf{Louise Kellogg and Lorraine Hwang: \textit{Advancing Earth Science
through Best Practices in Open Source Software: Computational Infrastructure for
Geodynamics}}. Lorraine Hwang presented experiences with the Computational
Infrastructure for Geodynamics (CIG), a community software with a worldwide user
base. Like others, their main goals include high usability, sustainability, and
reproducibility. As a means to achieve these goals, various communication
channels have been developed, such as mailing lists, wikis, workshops,
hackathons, tutorials, and webinars. In order to contribute to the
infrastructure, codes must adhere to specified minimum standards with the desire
that all codes are working toward target standards.
%, but ideals are also given to encourage reaching the aforementioned goals. 
These include, e.g., the use of version control, certain coding styles, the
presence and nature of code tests and documentation, and certain user workflows.

\item \textbf{Lorraine Hwang, Joe Dumit, Alison Fish, Louise Kellogg, Mackenzie
Smith, and Laura Soito: \textit{Software Attribution for Geoscience Applications
in the Computational Infrastructure for Geodynamics}}. In a second talk, Lorraine
Hwang mentioned a variety of ways to cite efforts within the framework, including
science papers, code papers, user manuals, and the CIG website. An analysis of
the resulting citations showed that $80\%$ of papers that use CIG codes mention
the code name, and about the same number includes a citation. Only about $20\%$
acknowledge CIG. Within the same sample of papers, about one fifth use an URL to
cite codes (including non-CIG codes), and only about one eighth specify the
version used. Compared to other codes, CIG seems to be much better cited. In
part, this is attributed to the fact that CIG requires that donated software
provide a citable paper specified in the User Manual. The project is working on
tools and methods to generate attribution information automatically.
%This,
%in part, is attributed to suggested citation forms communicated to the
%community, and runtime tools that help collecting a relevant citation list
%automatically.

>>>>

\item \textbf{Louise Kellogg and Lorraine Hwang: \textit{Advancing Earth Science
through Best Practices in Open Source Software: Computational Infrastructure for
Geodynamics}}. Lorraine Hwang presented experiences with the Computational
Infrastructure for Geodynamics (CIG)\footnote{\url{http://geodynamics.org/}}, a community software with a worldwide user
base. Like others, their main goals include high usability, sustainability, and
reproducibility. As a means to achieve these goals, various communication
channels have been developed, such as mailing lists, wikis, workshops,
hackathons, tutorials, and webinars. In order to contribute to the
infrastructure, codes must adhere to specified minimum standards with the desire
that all codes are working toward target standards.
%, but ideals are also given to encourage reaching the aforementioned goals. 
These include, e.g., the use of version control, certain coding styles, the
presence and nature of code tests and documentation, and certain user workflows.

\item \textbf{Lorraine Hwang, Joe Dumit, Alison Fish, Louise Kellogg, Mackenzie
Smith, and Laura Soito: \textit{Software Attribution for Geoscience Applications
in the Computational Infrastructure for Geodynamics}}. In a second talk, Lorraine
Hwang mentioned a variety of ways to cite efforts within the SAGA framework\footnote{\url{https://geodynamics.org/cig/projects/saga/}}, including
science papers, code papers, user manuals, and the CIG website. An analysis of
the resulting citations showed that $80\%$ of papers that use CIG codes mention
the code name, and about the same number includes a citation. Only about $20\%$
acknowledge CIG. Within the same sample of papers, about one fifth use an URL to
cite codes (including non-CIG codes), and only about one eighth specify the
version used. Compared to other codes, CIG seems to be much better cited. In
part, this is attributed to the fact that CIG requires that donated software
provide a citable paper specified in the User Manual. The project is working on
tools and methods to generate attribution information automatically.
%This,
%in part, is attributed to suggested citation forms communicated to the
%community, and runtime tools that help collecting a relevant citation list
%automatically.
